---
title: "Web Text Scrappping"
author: "Kylee Valencia"
date: "3/17/2022"
output: 
  html_document: 
    fig_width: 14
    fig_height: 8
editor_options: 
  chunk_output_type: inline
---

```{r}
loadpackageCompete<-function(x){
  install.packages(setdiff(x, rownames(installed.packages())))
  xfun::pkg_attach(x)
}
```


```{r warning=FALSE, include=FALSE}
# For Html text Processing
for_text_extraction<-c("rvest","robotstxt","XML","quanteda","tm","textclean")
loadpackageCompete(for_text_extraction)

# For text manipulation
for_text_analysisProcessing<-c("stringr","dplyr","tidyverse")
loadpackageCompete(for_text_analysisProcessing)
#For visualization
for_visual_dashboard<-c("ggplot2","plotly","paletteer")
loadpackageCompete(for_visual_dashboard)


```



#Source data to be scrapped
```{r}
scrap_minyak<- c(
                "nasional.kontan" = "https://nasional.kontan.co.id/news/soal-harga-minyak-goreng-mahal-mendagri-ini-kesalahan-saya?page=all",
                "money.kompas"  = "https://money.kompas.com/read/2022/03/23/065838326/cek-harga-minyak-goreng-jelang-ramadhan",
                "cnn.indo" = "https://www.cnnindonesia.com/ekonomi/20220302193301-92-766134/daftar-harga-komoditas-di-dunia-yang-naik-akibat-perang-rusia-ukraina",
                "BBC" = "https://www.bbc.com/indonesia/60837667",
                "ekonomi.bisnis" = "https://ekonomi.bisnis.com/read/20220307/12/1507833/harga-minyak-goreng-curah-naik-lagi-tembus-rp17100-per-liter",
                "dpr.go" = "https://www.dpr.go.id/berita/detail/id/38086/t/Harga+Minyak+Goreng+Harus+Diredam")
```



#Indonesia Stopword
```{r}
read.delim("https://raw.githubusercontent.com/SokKanaTorajd/indonesia-stopwords/main/indonesia-stopwords.txt",
           sep = "\n",
           header = T) %>% setNames("IndoStopWords") -> IndonesiaStopword
```


```{r}
IndonesiaStopword
```


#Indonesia SlangWord
```{r}
read.delim("https://raw.githubusercontent.com/yudiwbs/indonesian_slang/main/catatan_kata_sinonim.txt",
           sep="\n",
           header = F) %>% 
  setNames("IndoSlang") %>% rbind("migor=minyak goreng") -> IndonesiaSlang
IndonesiaSlang

```
#Cleaning slangword dictionary format
```{r}
str_split_fixed(string=IndonesiaSlang$IndoSlang, pattern = fixed("="), n=2) %>%
  data.frame() %>%
  setNames(c("Slang", "Formal")) %>%
  dplyr::mutate(Formal= gsub(x = Formal,"(<|>)", replacement = "")) ->
  IndonesiaSlang
```


```{r}
IndonesiaSlang %>% rbind(c("chain","rantai")) -> IndonesiaSlang
```



```{r}
IndonesiaSlang
```

#Count the word freq
```{r}
wordFreqG <- function(x){
  print(class(x))
  
  x %>%
    replace_internet_slang(slang = paste0("\\b", IndonesiaSlang$Slang, "\\b"), replacement = IndonesiaSlang$Formal) %>%
    VectorSource() %>%
    Corpus() %>%
    tm_map(removeWords, IndonesiaStopword$IndoStopWords) %>%
    tm_map(removeNumbers) %>%
    tm_map(removePunctuation) %>% 
    tm_map(stripWhitespace) %>%
    tm_map(stemDocument, language = "indonesian") %>%
    TermDocumentMatrix()%>%
    as.matrix() %>%
    rowSums() %>%
    sort(decreasing = TRUE) %>%
    data.frame() %>%
    setNames("freq")-> wordMinyakFreq

  return(wordMinyakFreq)
  
}

  

```


#Read html into text data
```{r}
turn_Text <- function(a){
  read_html(a ) %>% 
    html_elements("p") %>%
    html_text() %>% 
    tolower() %>%
    replace_internet_slang(slang = paste0("\\b", IndonesiaSlang$Slang, "\\b"), replacement = IndonesiaSlang$Formal) -> dataText
  
  return(dataText)
}
```


```{r}
WhoseBest <- c()
```


```{r}
for (i in scrap_minyak){
  tempData <- i %>% turn_Text()
  WhoseBest <- c(WhoseBest, tempData)
  
}
```



```{r}
WhoseBest %>% wordFreqG() -> FreqWord_Table
```

```{r}
FreqWord_Table

```


```{r}
library(readxl)

minyak_goreng_curah_harga_17_Feb_24_Mar_2022 <- read_excel("minyak goreng curah harga 17 Feb - 24 Mar 2022.xls")


```




```{r}
colNameRep <- function(ModifData){
  colnames(ModifData) %>% 
  gsub(pattern = "\\/",replacement = "-") -> colnames(ModifData)
  
  return(ModifData)
}
```


```{r}
basic_info<-function(df,varname=""){
  
             df%>% 
                     is.na() %>%
                     colSums() %>%
                     data.frame() %>%
                     setNames("Total_Missing_Value") -> new_Data
  
              return( new_Data %>%
                     mutate("Data_Type"=(lapply(df, class)%>%
                                            as.data.frame() %>%
                                            t %>%
                                            as.data.frame() %>% 
                                            setNames(c("DataType")) )$DataType) 
                     )
}
```


```{r}
NA24Rowname <- function(x){
  basic_info(x) %>% subset(Total_Missing_Value>=1) %>% rownames() %>% return()

}
```


```{r}
CleanTableXLS <- function(df){
  df %>% 
    colNameRep() %>%
     select(-"No.") -> df ;df %>%
     t() %>% 
    as.data.frame() %>% setNames(df[[1]]) -> df; df %>%
    subset(rownames(df)!="Provinsi") -> df; 
    df[df=="-"]=NA
    df %>%
    select(-(NA24Rowname(df))) -> df;
    
  return(df)
    
    
}
```


```{r}
convertDateandDouble <- function(DD){
  lapply(DD, as.double) %>% data.frame() %>%   
    mutate("Tanggal"=rownames(DD), .before=SEMUA.PROVINSI) ->testDD;
  testDD %>% 
  mutate_if(is.numeric, function(x) ifelse(is.na(x), median(x, na.rm = T), x))
  testDD$Tanggal = as.Date(testDD$Tanggal, "%d-%m-%Y")
  
  return(testDD)
}
```


```{r}
meltData <- function(TableD){
  
  data.table::melt(TableD, 
                   id.vars="Tanggal" , 
                   measure.vars = TableD %>%
                     select(-Tanggal) %>% 
                     colnames()) %>% 
                     setNames(c("Tanggal", "Provinsi", "Harga")) -> TableD
  return(TableD)
  
}

```



```{r echo=FALSE}
minyak_goreng_curah_harga_17_Feb_24_Mar_2022 %>% 
  colNameRep %>% 
  CleanTableXLS %>% 
  convertDateandDouble %>% 
  meltData -> Minyak_Curah_Harga
  
Minyak_Curah_Harga
  
```


```{r}
FreqWord_Table %>% 
  mutate(Words = rownames(FreqWord_Table), .before=freq) -> FreqWord_Table;

rownames(FreqWord_Table) = c(1:nrow(FreqWord_Table))
FreqWord_Table
```

```{r}
toSentence <- function(x){
  return(paste0(toupper(substr(x,1,1)), substr(x,2,str_length(x)) %>% tolower()))
}
```


```{r}
library(repr)
options(repr.plot.width = 20, repr.plot.height = 8)
FreqWord_Table %>% subset(!Words %in% c("minyak",
                                        "goreng",
                                        "dagang",
                                        "mendag",
                                        "masan",
                                        "usaha",
                                        "sawit",
                                        "sumber", 
                                        "gambar",
                                        "nomor",
                                        "teri",
                                        "persen",
                                        "bijak",
                                        "lutfi"
                                        )) %>% 
  mutate(Words = toSentence(Words)) %>%
  mutate(Words = case_when(Words=="Subsid" ~ "Subsidi",
                           Words=="Cpo" ~ "Crude Palm\nOil\n(CPO)",
                           Words=="Het" ~"HET",
                           Words=="Perintah" ~ "Pemerintah",
                           T ~ Words)) %>% 
  top_n(11) -> Words10Top

```

```{r}
list(PlotClus1Minyak, PlotClus2Minyak, PlotClus3Minyak) -> tempData

```


```{r}
interactPlotlyArea <- function(plDD, Area = "", colorP =paletteer_d("rcartocolor::Pastel")){
  plDD %>% ggplot(aes(Tanggal, Harga,col=Provinsi)) + 
  geom_line(size=0.7)+ geom_point(size=1.65 ) + 
  labs(title = paste("Harga Minyak Curah berdasarkan Data PIHPS (liter):",Area),
       y = "Harga (Rp)")+
  theme_light() + 
    theme(plot.title = element_text(face = "bold", size=10, hjust=0.5),
          axis.title.y = element_text(face="bold", size = 8),
          axis.title.x = element_text(face="bold", size = 8))+
    scale_color_manual(values=  colorP)-> plDD
  #facet_wrap(~Provinsi, scale="free") +

  return(plDD %>% ggplotly())
  
}
```



#Load desire color palette for plotting
```{r}
paletteer_d("basetheme::brutal") -> palet1
paletteer_d("beyonce::X90") -> palet2
paletteer_d("Polychrome::light") -> palet3
paletteer_d("ggthemes::Classic_Cyclic") -> palet4
paletteer_d("ggsci::default_ucscgb") ->palet5
palet6 <-paletteer_d("vapoRwave::vapoRwave")
palet6

palet1;palet2;palet3;palet4;palet5
```


#Plot without splitting categorical data
```{r}
interactPlotlyGeneral <- function(plDD, color="aliceblue"){
  plDD %>% ggplot(aes(Tanggal, Harga)) + 
  geom_line(size=0.7, color  = color)+ geom_point()  + 
  labs(title = paste("Harga Rata-Rata Minyak Curah berdasarkan Data PIHPS (liter)"))+
    theme_light()+ theme(legend.position = "none",
                         plot.title = element_text(hjust = 0.5,face = "bold", size=14),
                         axis.title.x = element_text(face="bold", size=11),
                         axis.title.y = element_text(face="bold", size=11))-> plDD
  #facet_wrap(~Provinsi, scale="free") +

  return(plDD %>% ggplotly())
  
}
```



Plot need to be make
[1] Top 9 Frequent word talk in Minyak Goreng
```{r}
Words10Top  %>%
  ggplot(aes(x=reorder(Words, -freq),
             y = freq, 
             fill = factor(freq, levels = factor(freq)%>%unique)))+ 
  geom_col(width = 0.55) +
  labs(x = "Popular Words",
       y="Frequency", 
       title = "Top 9 Popular Words about Minyak Goreng 2022",
       fill = "Word Intensity")+
  theme_linedraw()+
  theme(axis.text.x = element_text(angle = -18), 
        legend.title = element_blank(),
        plot.title = element_text(face = "bold", hjust = 0.5, size=17),
        axis.title.x = element_text(size=11, face="bold",margin = margin( l= 3)),
        axis.title.y = element_text(size=11, face="bold"))+
  scale_fill_manual(values = palet4)-> objectPopular
  objectPopular
```


[2] Plot Cluster for Minyak Curah
```{r}
ProvinsiMinyakCurah <- Minyak_Curah_Harga$Provinsi %>% as.character()

case_when(ProvinsiMinyakCurah=="DKI.JAKARTA" ~ "JAKARTA",
          ProvinsiMinyakCurah=="DI.YOGYAKARTA" ~"YOGYAKARTA",
          T ~ ProvinsiMinyakCurah) -> ProvinsiMinyakCurah

```


```{r}
ProvinsiMinyakCurah %>% unique
```


```{r}
cbind((Minyak_Curah_Harga$Provinsi %>% as.character() %>% unique), ProvinsiMinyakCurah %>% unique) %>% as.data.frame()
```
```{r}
Minyak_Curah_Harga$Provinsi <- Minyak_Curah_Harga$Provinsi %>% as.character()
```



```{r}
ProvinsiMinyakCurah %>% lapply(testChangeStr) %>% unlist() -> ProvinsiMinyakCurah

```

```{r}
ProvinsiClus1 <- c("Aceh", "Sumatera Utara", "Sumatera Barat",
                   "Riau", "Lampung", "Jambi",
                   "Banten", "Sumatera Selatan", "Jakarta")
ProvinsiClus2 <- c("Jawa Tengah", "Yogyakarta", "Jawa Barat",
                   "Jawa Timur", "Bali", "Nusa Tenggara Barat",
                   "Kalimantan Barat", "Kalimantan Tengah", "Kalimantan Utara" )
ProvinsiClus3 <- c("Kalimantan Timur", "Kalimantan Selatan", "Sulawesi Selatan",
                   "Sulawesi Tenggara", "Sulawesi Tengah", "Sulawesi Utara",
                   "Sulawesi Barat", "Maluku Utara", "Papua" )
```

```{r}
ProvinsiMinyakCurah %>% unique
```


```{r}

Minyak_Curah_Harga$Provinsi <- ProvinsiMinyakCurah


```


```{r}
Minyak_GorengCurah_df$Provinsi %>% unique
```


```{r}
plotGeneralMinyak <- Minyak_Curah_Harga %>% subset(Provinsi=="Semua Provinsi") 
PlotClus1Minyak <- Minyak_Curah_Harga %>% subset(Provinsi %in% ProvinsiClus1)
PlotClus2Minyak <- Minyak_Curah_Harga %>% subset(Provinsi %in% ProvinsiClus2)
PlotClus3Minyak <- Minyak_Curah_Harga %>% subset(Provinsi %in% ProvinsiClus3)
```


```{r}
PlotClus1Minyak$Provinsi %>% unique
PlotClus2Minyak$Provinsi %>% unique
PlotClus3Minyak$Provinsi %>% unique
```





```{r}
interactPlotlyGeneral(plotGeneralMinyak, color = "royalblue2")-> Minyak_Curah_RataRata_Provinsi
Minyak_Curah_RataRata_Provinsi
```

```{r}
Minyak_Curah_Clus1 <- interactPlotlyArea(PlotClus1Minyak, "\nArea Cluster 1", colorP = palet3)
Minyak_Curah_Clus2 <- interactPlotlyArea(PlotClus2Minyak, "\nArea Cluster 2", colorP = palet5)
Minyak_Curah_Clus3 <- interactPlotlyArea(PlotClus1Minyak, "\nArea Cluster 3", colorP = palet6)

Minyak_Curah_Clus1;Minyak_Curah_Clus2;
Minyak_Curah_Clus3
```


Plot For Top 9 Words
```{r}
Top9Words <- ggplotly(objectPopular)
Top9Words

```


```{r}
Map(function(x) x%>% select(Provinsi) %>% unique, DataFrameListHarga)
``` 


```{r}
testChangeStr <- function(x) {
  str_split(x, pattern = "\\.") %>%
    unlist() %>% lapply(toSentence) %>% paste(collapse = " ") -> newStr
  
  return(newStr)
}

```



```{r}
read_html("https://www.cpopc.org/") %>% 
  html_elements("table") %>% 
  html_table() -> CPOPCPalmOilPrice
CPOPCPalmOilPrice %>% as.data.frame() %>% select(-wdt_ID) ->CPOPCPalmOilPrice
CPOPCPalmOilPrice

```



```{r}
as.Date(CPOPCPalmOilPrice$Closing.date,"%d %b %Y") -> CPOPCPalmOilPrice$Closing.date
CPOPCPalmOilPrice
```


```{r}
basic_info(CPOPCPalmOilPrice)
```


```{r}
gsub(pattern = "\\,",x =  CPOPCPalmOilPrice$CPO.FOB.Indonesia, replacement = "") %>% as.double -> CPOPCPalmOilPrice$CPO.FOB.Indonesia

gsub(pattern = "\\,",x =  CPOPCPalmOilPrice$CPO.FOB.Malaysia, replacement = "") %>% as.double -> CPOPCPalmOilPrice$CPO.FOB.Malaysia

gsub(pattern = "\\,",x =  CPOPCPalmOilPrice$SBO.Rotterdam.ex.mill, replacement = "") %>% as.double -> CPOPCPalmOilPrice$SBO.Rotterdam.ex.mill
```


```{r}
basic_info(CPOPCPalmOilPrice)
```



```{r}
CPOPCPalmOilPrice %>% setNames(c("Tanggal", "CPO FOB Indonesia", "CPO FOB Malaysia", "SBO Rotterdam ex mill")) -> CPOPCPalmOilPrice
CPOPCPalmOilPrice
```



meltData <- function(TableD){
  
  data.table::melt(TableD, 
                   id.vars="Tanggal" , 
                   measure.vars = TableD %>%
                     select(-Tanggal) %>% 
                     colnames()) %>% 
                     setNames(c("Tanggal", "Provinsi", "Harga")) -> TableD
  return(TableD)
  
}


```{r}
library(data.table)
 data.table::melt(CPOPCPalmOilPrice, id.vars ="Tanggal", 
                  measure.vars = c("CPO FOB Indonesia", "CPO FOB Malaysia", "SBO Rotterdam ex mill")) %>% dplyr::rename("CPO Parlement"=2, "Price"=3) -> CPOPTable

```

```{r}
CPOPTable %>% ggplot(aes(x = Tanggal, y = Price, col = `CPO Parlement`))+
  geom_point() + geom_line(size=1)+ 
  labs(title = "Council of Palm Oil Producing Country",
       y = "Price in USD per metric-ton") +theme_light()+
  theme(plot.title = element_text(face = "bold", size = 14, hjust=0.5),
        axis.title.x = element_text(face = "bold", size=11),
        axis.title.y = element_text(face = "bold", size = 11))-> p
p%>% ggplotly() -> CPO_PalmOilPalement
CPO_PalmOilPalement
```



##Proof of in global Oil price beside palm oil also rise significanly "https://www.bpdp.or.id/CPO_rotterdam.php"

```{r}
Crude_Palm_Oil_Futures_Historical_Data_15_Feb_24_March <- read.csv("Crude Palm Oil Futures Historical Data 15 Feb - 24 March.csv")
Palm_Oil_Price_17Feb2021_24March2021 <- read.csv("Palm Oil Price 17Feb2021-24March2021.csv")
```


```{r}
Crude_Palm_Oil_Futures_Historical_Data_15_Feb_24_March

Palm_Oil_Price_17Feb2021_24March2021

```



```{r}

Crude_Palm_Oil_Futures_Historical_Data_15_Feb_24_March %>% 
  dplyr::rename("Tanggal" = ï..Date) %>% select(-"Change..") -> Crude_Palm_Oil_Futures_Historical_Data_15_Feb_24_March

Palm_Oil_Price_17Feb2021_24March2021 %>% dplyr::rename("Tanggal" = "Date") -> Palm_Oil_Price_17Feb2021_24March2021

Crude_Palm_Oil_Futures_Historical_Data_15_Feb_24_March

Palm_Oil_Price_17Feb2021_24March2021

```

```{r}
Crude_Palm_Oil_Futures_Historical_Data_15_Feb_24_March$Vol.= NULL
Palm_Oil_Price_17Feb2021_24March2021$Volume = NULL

```


```{r}
Palm_Oil_Price_17Feb2021_24March2021

Crude_Palm_Oil_Futures_Historical_Data_15_Feb_24_March
```


```{r}
basic_info(Crude_Palm_Oil_Futures_Historical_Data_15_Feb_24_March)
basic_info(Palm_Oil_Price_17Feb2021_24March2021)
```



```{r}

Crude_Palm_Oil_Futures_Historical_Data_15_Feb_24_March$Tanggal  %>% 
  as.Date("%b %d, %Y") -> Crude_Palm_Oil_Futures_Historical_Data_15_Feb_24_March$Tanggal
Crude_Palm_Oil_Futures_Historical_Data_15_Feb_24_March
```


```{r}
Palm_Oil_Price_17Feb2021_24March2021$Tanggal %>% 
  as.Date("%m/%d/%y") -> Palm_Oil_Price_17Feb2021_24March2021$Tanggal
Palm_Oil_Price_17Feb2021_24March2021
```

```{r}
Crude_Palm_Oil_Futures_Historical_Data_15_Feb_24_March[c("Price","Open","High","Low")] %>% 
  Map( f = function(x){
  x %>% gsub(pattern = "\\,", replacement = "") %>% as.double()
}) %>% as.data.frame() ->  Crude_Palm_Oil_Futures_Historical_Data_15_Feb_24_March[c("Price","Open","High","Low")]
```

```{r paged.print=TRUE}
Crude_Palm_Oil_Futures_Historical_Data_15_Feb_24_March
```


```{r warning=FALSE}
data.table::melt(Crude_Palm_Oil_Futures_Historical_Data_15_Feb_24_March, id.vars="Tanggal",
                           measure.vars = c("Price","Open","High","Low")) %>% dplyr::rename("State" = 2, Cost = 3) -> CPO_15
```


```{r warning=FALSE}
data.table::melt(Palm_Oil_Price_17Feb2021_24March2021, id.vars = "Tanggal" ,
                 measure.vars = c("Close","Open","High","Low")) %>% dplyr::rename("State" = 2, Cost = 3) -> Future_PalmOil_data
```


```{r}
CPO_15 %>% ggplot(aes(x = Tanggal, y = Cost, col = State))+ geom_point() +
  geom_line(size=.7) + theme_light() + labs(title = "Investing Website investment Palm Oil Price India",
                                            x = "Date") +
  theme(plot.title = element_text(face = "bold", hjust = 0.5, size=14),
        axis.title.x = element_text(face="bold", size=11),
        axis.title.y = element_text(face = "bold", size=11)) -> PalmOilInvestI

PalmOilInvestI %>% ggplotly() -> PalmOilInvestI
PalmOilInvestI
```



```{r}
Future_PalmOil_data %>% ggplot(aes(x = Tanggal, y = Cost, col = State))+ geom_point() +
  geom_line(size=.7) + theme_light() + labs(title = "Market Insider Investment Palm Oil Price",
                                            x = "Date") +
  theme(plot.title = element_text(face = "bold", hjust = 0.5, size=14),
        axis.title.x = element_text(face="bold", size=11),
        axis.title.y = element_text(face = "bold", size=11)) -> PalmOilInvestII

PalmOilInvestII %>% ggplotly() -> PalmOilInvestII
PalmOilInvestII
```

## Contoh cara melakukan save plot kedalam bentuk html document

```{r eval=FALSE, include=FALSE}
htmlwidgets::saveWidget(interactPlotly(DataFrameListHarga[[1]],
                                       names(DataFrameListHarga[1])),
                        "nama file.html")
```


## Start dari line dibawah ini kode jangan dijalankan dikarenakan untuk mengexport plot dari R 
   ke akun chart-studio plotly


```{r eval=FALSE, include=FALSE}
MyPlotly_API_Key = "J7eD0B5c9KPa9JJSGUWK"
MyPlotly_API_Token = "tx4g0r2r1e"

MyPlotly_Username = "Trumpet_Me"


Sys.setenv("plotly_username" = MyPlotly_Username)
Sys.setenv("plotly_api_key" = MyPlotly_API_Key)
```


```{r eval=FALSE, include=FALSE}
options(browser = "false")
api_create(Top9Words, filename = "Capstone Top 9 Words Corelated to Minyak Sawit", fileopt = "overwrite")
api_create(Minyak_Curah_Clus1, filename = paste("Capstone", "Minyak Curah Area C1"), fileopt = "overwrite")
api_create(Minyak_Curah_Clus2, filename = paste("Capstone", "Minyak Curah Area C2"), fileopt = "overwrite")
api_create(Minyak_Curah_Clus3, filename = paste("Capstone", "Minyak Curah Area C3"), fileopt = "overwrite")
api_create(Minyak_Curah_RataRata_Provinsi, filename = paste("Capstone", "Minyak Curah Rata-rata di Indonesia"), fileopt = "overwrite")
api_create(PalmOilInvestI, filename = paste("Capstone", "India Investment Palm Oil Platform"), fileopt = "overwrite")
api_create(PalmOilInvestII, filename = paste("Capstone", "Market Insider Invesment Palm Oil Platform"), fileopt = "overwrite")
```



```{r eval=FALSE, include=FALSE}
options(browser = 'false')
api_create(CPO_PalmOilPalement, filename = paste("Capstone", "Council of Palm oil Producer Price Data (barrel)"), fileopt = "overwrite")
```

